## M =  `r M`

```{r load_aggregated_Stan_output, message=FALSE}
#res_list <- load_aggregated_output(obsFolder = obsFolder, M = M, m = m)
#list2env(load_aggregated_output(obsFolder = obsFolder, M = M, m = m), .GlobalEnv)


invisible(list2env(load_aggregated_Stan_output(obsFolder, M), .GlobalEnv))
# contains results_separate_Stan and resultsOverall_Stan

```


```{r missing, echo=FALSE}
stan_res_missing <- sum(is.na(resultsOverall_Stan[,1]))
total_missing_stan <- total_missing_stan + stan_res_missing
```



\# of missing results: `r stan_res_missing`

\# Rhat > 1.01: `r sum(results_separate_Stan[,"Rhat", ] > 1.01, na.rm = TRUE)` (out of 200)

range of max. duration in seconds: 
(`r round(range(resultsOverall_Stan[,"maxDuration"], na.rm = TRUE), digits = 1)`),
 median: `r round(median(resultsOverall_Stan[,"maxDuration"], na.rm = TRUE), digits = 1)`

median multivarESS: `r round(median(resultsOverall_Stan[,"multivarESS"], na.rm = TRUE), digits = 0) `

```{r stan_plots}
plot_Stan_hist <- function(results_separate_Stan, resultsOverall_Stan=NULL, result, 
                           third_plot=NULL, add_true = FALSE){
  par(mar=c(3, 4, 0.1, 2))
  num_plots <- 2 + length(third_plot)
  layout(matrix(1:num_plots, ncol = num_plots))
  for(i in 1:length(par_names)){
    hist(results_separate_Stan[, result, i], main = '', xlab = '', las = 1)
    title(xlab = par_names[i], cex.lab = 1, line = 2)
    if(add_true){
      abline(v=true_values[i], col = 2)
      legend("topright", legend = "true value", col = 2, bty = "n", lty = 1, cex = .7, seg.len = 1)
    }
  }
  if(length(third_plot)){
    hist(resultsOverall_Stan[, third_plot], main = '', xlab = '', las = 1)
    title(xlab = third_plot, cex.lab = 1, line = 2)
  }
}

plot_Stan_density <- function(results_separate_Stan, resultsOverall_Stan=NULL, result, 
                           third_plot=NULL, add_true = FALSE){
  par(mar=c(3, 4, 0.1, 2))
  num_plots <- 2 + length(third_plot)
  layout(matrix(1:num_plots, ncol = num_plots))
  for(i in 1:length(par_names)){
    plot(density(results_separate_Stan[, result, i], na.rm = TRUE), main = '', xlab = '', las = 1)
    title(xlab = par_names[i], cex.lab = 1, line = 2)
    if(add_true){
      abline(v=true_values[i], col = 2)
      legend("topright", legend = "true value", col = 2, bty = "n", lty = 1, cex = .7, seg.len = 1)
    }
  }
  if(length(third_plot)){
    plot(density(resultsOverall_Stan[, third_plot], na.rm = TRUE), main = '', xlab = '', las = 1)
    title(xlab = third_plot, cex.lab = 1, line = 2)
  }
}

fig_height_2p <- 2
fig_height_3p <- 1.8
```


The following sections show density plots of the respective statistic calculated for the `r N` simulated datasets.

#### Posterior mean
```{r mean_stan, fig.height=fig_height_2p}
#plot_Stan_hist(results_separate_Stan, resultsOverall_Stan, "mean", third_plot=NULL)
plot_Stan_density(results_separate_Stan, resultsOverall_Stan, "mean", add_true = TRUE)
```

#### Posterior median
```{r median_stan, fig.height=fig_height_2p}
plot_Stan_density(results_separate_Stan, resultsOverall_Stan, "median", add_true = TRUE)
```

#### Optimized value
```{r opt_result_stan, fig.height=fig_height_2p}
plot_Stan_density(results_separate_Stan, resultsOverall_Stan, "opt_result", add_true = TRUE)
```

\newpage
#### Posterior variance and covariance
```{r variance_stan, fig.height=fig_height_3p}
plot_Stan_density(results_separate_Stan, resultsOverall_Stan, "variance", 
                  third_plot = "covariance")
```

#### Effective sample size
```{r ESS_stan, fig.height=fig_height_3p}
plot_Stan_hist(results_separate_Stan, resultsOverall_Stan, "ESS_coda", 
                  third_plot = "multivarESS")
```
